Return of the Linguist:\\Toward scalable parallel corpus generation for machine translation

### 2016-07-11 doc/paper.tex
AMTA was extended AGAIN

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{5}{*}{BLEU $\uparrow$}
& Official IWSLT14 baseline  & 11.2 & -   & -   & - \\
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & 10.8 & 0.3 & 0.3 & 0.00 \\
& Training: 2015 corpus & 11.5 & 0.3 & 0.3 & 0.30 \\
& Training: 2015 corpus (post-edited) & \textbf{11.7} & 0.3 & 0.1 & 0.01 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 11.0 & 0.3 & 0.2 & 0.00 \\
\hline
\multirow{5}{*}{TER $\downarrow$}
& Official IWSLT14 baseline & 77.0 & -   & -   & - \\
& Our baseline & 76.2 & 0.8 & 0.3 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & 83.4 & 1.0 & 0.5 & 0.00 \\
& Training: 2015 corpus & 76.4 & 0.8 & 0.5 & 0.26 \\
& Training: 2015 corpus (post-edited) & \textbf{75.6} & 0.8 & 0.0 & 0.00 \\
%& system 4 & 82.7 & 1.0 & 0.8 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

@@

Table~\ref{tab:multeval_tst2010} gives results evaluated on the original {\small \tt tst2010} data set.
The IWSLT 2015 training corpus {\small \tt train2015} did not produce a significant improvement over the IWSLT 2014 baseline.
Although {\small \tt train2015} includes an additional \textasciitilde 30,000 lines of in-domain data, increasing the corpus size by \textasciitilde 17\%, it is also plagued by the new problem of missing fragments and resulting misaligned sentences mentioned in Section~\ref{subsec:post_edited}.
Accordingly, post-editing \textasciitilde 7500 lines (3.6\%) of {\small \tt train2015} produced a small but significant improvement in scores,\footnote{
This might look like a proportional improvement in BLEU, but gains were found to come in discrete steps during the editing process. This is thought to be due to the non-parametric nature of SMT, with changes in scores only occurring when there are appreciable changes to the parts of the probability tables that are relevant to the test set.
} demonstrating the importance of corpus quality, not just quantity.
Finally, unlike Table~\ref{tab:tst2010}, post-editing the MERT tuning development set {\small \tt dev2010} surprisingly makes things strictly worse.
The effect of corrective post-editing tuning corpora appears to be relatively unpredictable, guiding the MERT optimizer to different local optima with varying out-of-sample performance.
Whereas input-domain noise can play a role similar to regularization in methods such as denoising autoencoders \mycitep{bengio:2008}, the effect of ``large-amplitude'' noise from mistranslated or misaligned parallel corpora is unclear, and it may warrant further investigation in other models.

@@

% NOTE
% +0.3 BLEU -0.6 TER from post-editing the entire training corpus, esp the new 2015 additions (~25000 lines)
% +0.1 BLEU -0.2 TER from ``snoop-editing'' Moses output lexical items only. cheating takes you FAR...
\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System (all with post-edited {\small \tt tst2010}) & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{4}{*}{BLEU $\uparrow$}
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & \textbf{11.9} & 0.3 & 0.1 & 0.00 \\
& Training: 2015 corpus & 11.4 & 0.3 & 0.2 & 0.44 \\
& Training: 2015 corpus (post-edited) & 11.6 & 0.3 & 0.2 & 0.01 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & \textbf{12.2} & 0.3 & 0.1 & 0.00 \\
\hline
\multirow{4}{*}{TER $\downarrow$}
& Our baseline & 70.6 & 0.4 & 0.5 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & 75.1 & 0.5 & 0.3 & 0.00 \\
& Training: 2015 corpus & 70.1 & 0.4 & 0.3 & 0.00 \\
& Training: 2015 corpus (post-edited) & \textbf{69.7} & 0.4 & 0.2 & 0.00 \\
& + generated & & & &  \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 74.7 & 0.5 & 0.2 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

\caption{\label{tab:multeval_tst2010_fixed} % \caption[LoF entry] would allow multi-paragraph caption... \hspace{0.6 cm} to indent
%\-\caption[LoF entry]{ \label{tab:multeval_tst2010}
MultEval results obtained as described in Table~\ref{tab:multeval_tst2010}, but evaluated on the post-edited {\small \tt tst2010} data set.
} % caption
\end{table}

%\pagebreak
Now we discuss Table~\ref{tab:multeval_tst2010_fixed}, for which we now as a test set the previously post-edited tst2010.
Unlike the tuning set, post-editing the test set is expected to have a more predictable effect.
Namely, correcting lines in the test set as described in Section~\ref{subsec:case_study} is expected to improve scores compared with Table~\ref{tab:multeval_tst2010}, as it should generally be easier for the MT system to reproduce lines that have not been grossly mistranslated.
This does indeed seem to be the case, with a more pronounced effect for TER scores.% with most runs except for the uncorrected 2015 training corpus

%Baseline's TER score changes by about 10\% relative to Table~\ref{tab:multeval_tst2010}, but BLEU doesn't change as much.
This time there is a statistically significant improvement for train2015, but only in the TER score and not for BLEU.
Apparently, BLEU scores are more robust than TER with respect to changes in training, tuning, and test corpora.
Post-editing train2015 again leads to further improvement in both metrics.

Unlike Table~\ref{tab:multeval_tst2010}, post-edited dev2010 no longer makes everything uniformly worse. 
Instead, and as in Table~\ref{tab:tst2010}, post-editing of the tuning set obtains slightly better BLEU at the expense of much worse TER. 
This again emphasizes the fact that tuning set noise can affect bottom-line performance in relatively unpredictable ways.

Table~\ref{tab:multeval_tst2010_fixed} also has some initial results from the ``example-based'' mode of our generator.
[Should I add an example of the meta-templates, to show how easy they are to write?]
These examples focus on quality instead of quantity and so there aren't many of them.
Started by looking for non-compositional sentences in poorly-scoring training pairs.
Alternative translations to some liberal (but not incorrect) translations were also included.
This was only possible after post-editing to clear out the noise.
They were simply concatenated to the end of the training corpus.
The results almost certainly suck.
To better direct future efforts, we perform some data snooping.
We are looking for at least a partial answer to the question, what makes a corpus in-domain?

Maybe we just to generate more data at scale. 
But should we scale up lexical data or syntactic data? 
To address this question, we resort to data snooping.

@@

For lexical snooping, we selected \textasciitilde 100 mistranslated or OOV words from the baseline translation and used the rule-based mode of our generator to generate \textasciitilde 30000 sentences with OOV words for concatenation.
This snooping-generated data doesn't make a dent, and in fact makes things slightly worse (although TER is within error bars).
So nonsensical sentences of OOV words does NOT help - or even if it does, the nonsense-noise drowns it out.

Taken together, these snooping results reinforce the sentiment from the end of Section~\ref{sec:experiments} that future scaled-up work on our generator should focus on the ``example-based'' approach.
Thus  you should focus on the example-based half.

>>>>

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{5}{*}{BLEU $\uparrow$}
& Official IWSLT14 baseline  & 11.2 & -   & -   & - \\
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & 10.8 & 0.3 & 0.3 & 0.00 \\
& Training: 2015 corpus & 11.5 & 0.3 & 0.3 & 0.30 \\
& Training: 2015 corpus (post-edited) & \textbf{11.9} & 0.3 & 0.0 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 11.0 & 0.3 & 0.2 & 0.00 \\
\hline
\multirow{5}{*}{TER $\downarrow$}
& Official IWSLT14 baseline & 77.0 & -   & -   & - \\
& Our baseline & 76.2 & 0.8 & 0.3 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & 83.4 & 1.0 & 0.5 & 0.00 \\
& Training: 2015 corpus & 76.4 & 0.8 & 0.5 & 0.26 \\
& Training: 2015 corpus (post-edited) & \textbf{75.2} & 0.8 & 0.0 & 0.00 \\
%& system 4 & 82.7 & 1.0 & 0.8 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

@@

Table~\ref{tab:multeval_tst2010} gives results evaluated on the original {\small \tt tst2010} data set.
The IWSLT 2015 training corpus {\small \tt train2015} did not produce a significant improvement over the IWSLT 2014 baseline.
Although {\small \tt train2015} includes an additional \textasciitilde 30,000 lines of in-domain data, increasing the corpus size by \textasciitilde 17\%, it is also plagued by the new problem of missing fragments and resulting misaligned sentences mentioned in Section~\ref{subsec:post_edited}.
Accordingly, post-editing \textasciitilde 7500 lines (3.6\%) of {\small \tt train2015} produced a small but significant improvement in scores, \footnote{
This might look like a proportional improvement in BLEU, but gains were found to come in discrete steps during the editing process. 
This is thought to be due to the non-parametric nature of SMT, with changes in scores only occurring when there are appreciable changes to the parts of the probability tables that are relevant to the test set.
It remains to be seen what effect post-editing of training, tuning, and test corpora would have on parametric systems like recent deep-learning based MT methods \mycitep{sutskever:2014,bengio:2014}, in which all training examples contribute to the same shared connection weight matrices.
} demonstrating the importance of corpus quality, not just quantity.
Finally, unlike Table~\ref{tab:tst2010}, post-editing the MERT tuning development set {\small \tt dev2010} surprisingly makes things strictly worse.
The effect of corrective post-editing tuning corpora appears to be relatively unpredictable, guiding the MERT optimizer to different local optima with varying out-of-sample performance.
Whereas input-domain noise can play a role similar to regularization in methods such as denoising autoencoders \mycitep{bengio:2008}, the effect of ``large-amplitude'' noise from mistranslated or misaligned parallel corpora is unclear, and it may warrant further investigation in other models.

% NOTE
% +0.3 BLEU -0.6 TER from post-editing the entire training corpus, esp the new 2015 additions (~25000 lines)
% +0.1 BLEU -0.2 TER from ``snoop-editing'' Moses output lexical items only. cheating takes you FAR...
\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System (all with post-edited {\small \tt tst2010}) & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{5}{*}{BLEU $\uparrow$}
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & \textbf{11.9} & 0.3 & 0.1 & 0.00 \\
& Training: 2015 corpus & 11.4 & 0.3 & 0.2 & 0.44 \\
& Training: 2015 corpus (post-edited) & \textbf{11.9} & 0.3 & 0.2 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & \textbf{12.2} & 0.3 & 0.1 & 0.00 \\
& + generated & \textbf{11.9} & 0.3 & 0.1 & 0.00 \\ 
\hline
\multirow{5}{*}{TER $\downarrow$}
& Our baseline & 70.6 & 0.4 & 0.5 & - \\
& Tuning: {\small \tt dev2010} (post-edited) & 75.1 & 0.5 & 0.3 & 0.00 \\
& Training: 2015 corpus & 70.1 & 0.4 & 0.3 & 0.00 \\
& Training: 2015 corpus (post-edited) & 69.4 & 0.4 & 0.2 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 74.7 & 0.5 & 0.2 & 0.00 \\
& + generated & \textbf{69.2} & 0.4 & 0.1 & 0.00 \\ 
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

\caption{\label{tab:multeval_tst2010_fixed} % \caption[LoF entry] would allow multi-paragraph caption... \hspace{0.6 cm} to indent
%\-\caption[LoF entry]{ \label{tab:multeval_tst2010}
MultEval results obtained as described in Table~\ref{tab:multeval_tst2010}, but evaluated on the post-edited {\small \tt tst2010} data set.
For the ``+ generated'' system, \textasciitilde 5000 lines from the ``example-based'' mode of our generator were concatenated to the post-edited 2015 training corpus.
} % caption
\end{table}

%\pagebreak
For Table~\ref{tab:multeval_tst2010_fixed}, the test set is changed to the previously post-edited tst2010.
Unlike its use as a tuning set in Section~\ref{subsec:case_study}, post-editing the test set is expected to have a more predictable effect.
Namely, translation corrections are expected to improve scores compared with Table~\ref{tab:multeval_tst2010}, as it should generally be easier for the MT system to reproduce lines that have not been grossly mistranslated.
This does indeed seem to be the case, with a more pronounced effect for TER scores.% with most runs except for the uncorrected 2015 training corpus

%Baseline's TER score changes by about 10\% relative to Table~\ref{tab:multeval_tst2010}, but BLEU doesn't change as much.
With the post-edited test set, there is now a small but statistically significant improvement in the TER score when using the unedited 2015 training corpus.
BLEU scores, on the other hand, appear to be more robust than TER with respect to changes in the test corpus.
Post-editing the training corpus again leads to further improvement in both metrics.

With the post-edited test set, post-editing of the tuning set {\small \tt dev2010} no longer makes everything uniformly worse, unlike Table~\ref{tab:multeval_tst2010}.
Instead, and as was the case when evaluating on {\small \tt tst2014} in Table~\ref{tab:tst2010}, post-editing of the tuning set in this case results in slightly improved BLEU at the expense of much worsened TER. 
This again emphasizes the fact that tuning set noise can affect bottom-line performance in relatively unpredictable ways.

The ``+ generated'' entry in Table~\ref{tab:multeval_tst2010_fixed} shows initial results using the quality-oriented ``example-based'' mode of our generator.
The starting point for template construction was non-compositional translations from the 2015 training corpus with high TER scores, which was only practical after post-editing to remove the clerical-like errors described in Section~\ref{subsec:case_study}.
The basic rationale is that poorly scoring training sentences are ones that the model has not fully ``learned'' yet.
Alternative translations to some liberal (but not incorrect) translations were also included.
As there were relatively few of them compared with Table~\ref{tab:results}, the generated sentences here were simply concatenated to the end of the training corpus.

To better direct future efforts, we perform some data snooping.
We are looking for at least a partial answer to the question, what makes a corpus in-domain?

Maybe we just to generate more data at scale. 
But should we scale up lexical data or syntactic data? 
To address this question, we consider the taboo practice of data snooping.

@@

@@

For lexical snooping, we selected \textasciitilde 100 mistranslated or OOV words from the baseline translation and used the rule-based mode of our generator to generate \textasciitilde 30000 sentences with OOV words for concatenation.
This snooping-generated data doesn't make a dent, and in fact makes things slightly worse (although TER is within error bars).
So nonsensical sentences of OOV words does NOT help - or even if it does, the nonsense-noise drowns it out.
More generally, it seems that although nonsensical sentences like Chomsky's ``colorless green ideas sleep furiously'' are fully licensed by English grammar, they can be detrimental practical NLP applications like MT that operate on naturally occurring sentences at test time.
Even when using an in-domain lexicon, their syntax can be sufficiently out-of-domain to result in a net loss of performance.

Taken together, these snooping results reinforce the sentiment from the end of Section~\ref{sec:experiments} that future scaled-up work on our generator should focus on the ``example-based'' approach.
Thus you should focus on the example-based half.
Moreover, the relative unimportance of OOV words suggests that the lexical databse need not be THAT exhaustive.
